\documentclass[12pt]{exam}

\printanswers
%\noprintanswers

% Change margin size
%\usepackage[margin=1in]{geometry}   
 
\usepackage{amsmath}
% \binom{n}{k}

\usepackage{graphicx}

\begin{document}

\textbf{Worksheet - 18 Feb 2020}
\hfill
\textbf{STAT 50 - Prof. Fitzgerald}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{5mm}

\begin{itemize}

\item
Law of Total Probability
\[
P(A) = P(A \cap B) + P(A \cap B^C) = P(A | B) P(B) + P(A | B^C) P(B^C)
\]

\item
Bayes Rule
\[
P(B | A) = \frac{P(A | B) P(B)}{P(A)}
\]

\end{itemize}

\begin{questions}

\question
Chef Joe makes delicious i.i.d. pancakes that vary slightly in heights.
The mean pancake height is 0.5 inch, and the standard deviation is 0.1 inch.
He serves them on i.i.d. plates that stand, on average, 0.3 inches off the top of the table, with standard deviation 0.02 inches.

\begin{parts}
\part
What is the mean height above the table for a stack of 5 pancakes?

\vfill
\part
What is the standard deviation of the height above the table for a stack of 5 pancakes?

\vfill
\part
Joe calculates the average height of 9 pancakes.
What is the mean and standard deviation of the average height?

\end{parts}
\vfill
\newpage
\question
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Students are taking a multiple choice exam.
About 60\% of the students know the material well.
If the student knows the material well, then the probability that they answer correctly is 0.9.
If they don't know the material well, then the probability that they answer correctly is 0.4.

\begin{parts}
\part
If a student answers one question correctly, what's the probability that they know the material well?

\vfill
\part
If a student answers 2 of 3 questions correctly, what's the probability that they know the material well?

\vfill
\part
If a student answers 2 of 3 questions correctly, what's the probability that they do not know the material well?

\vfill
\part
Based on these numbers, how effective is a 3 question multiple choice exam in measuring individual student performance?


\vfill
\part
Let $n$ be the number of questions on the exam.
If a student answers $c$ questions correctly, what's the probability that the student knows the material well?

\vfill
\part
How many questions need to be on an exam such that if a student answers all correctly, the probability that they know the material well is at least 0.99?


\end{parts}

\vfill

\end{questions}
\end{document}
