\documentclass[12pt, addpoints]{exam}

\printanswers
%\noprintanswers

% Change margin size
%\usepackage[margin=1in]{geometry}   
 
\usepackage{amsmath}
% \binom{n}{k}

\usepackage{graphicx}

\begin{document}

\textbf{Quiz - 7 February 2020}
\hfill
\textbf{STAT 50 - Prof. Fitzgerald}

\vspace{10mm}
 
\makebox[\textwidth]{Name:\enspace\hrulefill}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{5mm}

Please show your work. Here are some relevant formulas:

\[
n! = n (n-1) (n-2)... (3)(2)(1)
\qquad \qquad
\binom{n}{k} = \frac{n!}{k!(n-k)!}
\]

\begin{questions}

\question[5]

\emph{from homework}

8 new graduates are hired by an engineering firm.
Each is assigned at random to one of eight cubicles arranged in a row in the back of the room that houses the engineering staff.
2 of the graduates are Bill and Cathy.
What is the probability that they are assigned adjacent cubicles?

\begin{solution} 
The total number of pairs of cubicles is $\binom{8}{2} = \frac{8!}{6! 2!} = \frac{8 \cdot 7}{2} = 28$.
Each is equally likely to be chosen.
Of these pairs, seven are adjacent.
Therefore, the probability that an adjacent pair of cubicles is selected is $\frac{7}{28} = 0.25$.
\end{solution}
\vspace{\stretch{2}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\question 

A bicycle rental shop has 4 bikes, all different colors.
4 friends visit and rent the bikes.

\begin{parts}

\part[3]
How many ways are there to assign bikes to the friends?

\begin{solution} 
Line the bikes up in order.
There are $4! = 4 \cdot 3 \cdot 2 \cdot 1 = 24$ ways to line the friends up with the bikes, and this is all possible assignments.
\end{solution}
\vspace{\stretch{1}}

\part[2]

What's the probability that a particular friend, Anna, is assigned the green bike?
Assume all assignments are equally likely.

\begin{solution} 
If we assign Anna to the green bike, there are now three friends and three bikes.
As above, there are $3! = 3 \cdot 2 \cdot 1 = 6$ ways to assign the friends to bikes.
The probability Anna rides the green bike is $\frac{6}{24} = 0.25$.

More intuitively, Anna is equally likely to be assigned any of the four bikes, so the probability is $\frac{1}{4}$.
\end{solution}
\vspace{\stretch{1}}

\end{parts}

\end{questions}

\newpage
\begin{center}
\gradetable[v][questions]
\end{center}

\end{document}
