\documentclass[12pt, addpoints]{exam}

\printanswers
%\noprintanswers

% Change margin size
%\usepackage[margin=1in]{geometry}   
 
\usepackage{amsmath}
% \binom{n}{k}

\usepackage{graphicx}

\begin{document}

\textbf{Quiz - 14 February 2020}
\hfill
\textbf{STAT 50 - Prof. Fitzgerald}

\vspace{10mm}
 
\makebox[\textwidth]{Name:\enspace\hrulefill}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{5mm}

Please show your work. Here are some relevant formulas:

\begin{itemize}
\item
Definition of conditional probability:
$P(A | B) = \frac{P(A \cap B)}{P(B)}$

\item
Probability of event not happening:
$P(A^C) = 1 - P(A)$

\item
For $A,B$ independent events,
$P(A \cap B) = P(A) P(B)$.
\end{itemize}

\begin{questions}

\question[3]

\emph{from homework}

Items are inspected for flaws by two quality inspectors.
If a flaw is present, it will be detected by the first inspector with probability 0.91, and by the second inspector with probability 0.7.
Assume the inspectors function independently.

If an item has a flaw, what is the probability that it will be found by both inspectors?

\begin{solution} 

Let A denote the event that the flaw is found by the first inspector, and let B denote the event that the flaw is found by the second inspector.

\[
P(A \cap B) = P(A)P(B) = (0.91)(0.7) = 0.637
\]

\end{solution}
\vspace{\stretch{1}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\question 

Jack plans to purchase roses from the flower stand or the supermarket for his significant other on Valentine's Day, if they're not sold out.
The probability that the flower stand is out of roses is 0.15.
The probability that the flower stand and the supermarket are both out roses is 0.1.

\begin{parts}

\part[4]
What's the probability that the supermarket is out of roses, given that the flower stand is out of roses?

\begin{solution} 
Let $F$ be the event the flower stand is out of roses, and $S$ be the event that the supermarket is out of roses.

\[
P(S | F) = \frac{P(S \cap F)}{P(F)} = \frac{0.1}{0.15} = \frac{2}{3}
\]
\end{solution}
\vspace{\stretch{1}}

\part[3]

What's the probability that Jack is able to purchase roses?

\begin{solution} 
He can purchase roses only if both stores are not out roses.

Formally, $P( (S \cap F)^C ) = 1 - P(S \cap F) = 1 - 0.1 = 0.9$

\end{solution}
\vspace{\stretch{1}}


\end{parts}

\end{questions}

\newpage
\begin{center}
\gradetable[v][questions]
\end{center}

\end{document}
